From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-19 Pi+/paper/reversible1.tex
Text about denotational semantics

\noindent A simple denotational semantics of $\Pi$ can be specified by mapping each type to a finite set and each
combinator to a permutation between finite sets.

>>>>

\noindent A simple denotational semantics of $\Pi$ can be specified by mapping each type to a finite set and each
combinator to a bijection between finite sets, that is, a permutation.

Functions with finite sets as domains are finitely supported, that is, their outputs can be tabulated using the
canonical ordering on $\Fin[n]$. For bijections, this gives a listed permutation. By observing the action of the
combinators on the values of the finite set, we can define a denotational semantics which constructs the bijection.

\note{\(\Fin[n] \to A \eqv \type{Vec_{n}}(A)\)}

An alternative point of view is to work in the category of finite sets and functions, $\SetFin$, which is the category
freely generated by finite coproduct completion of the terminal category. Objects of $\SetFin$ can be identified with
sets of fixed cardinality, that is, $\Fin[n] \defeq \Set{0,1,\ldots,n-1}$. $\SetFin$ has finite coproducts and products,
which lets us interpret the types of $\PiLang$. Combinators are intepreted as morphisms in $\SetFin$, but we have to
restrict to invertible morphisms, that is, isomorphisms. This gives the \emph{groupoid} of finite sets and bijections,
$\BFin \defeq \mathsf{core}(\SetFin)$. The isomorphisms satisfied by coproducts and products in $\SetFin$ lift to
$\BFin$, but they're no longer categorical coproducts and products. They give two symmetric monoidal tensor products on
$\BFin$, the additive and multiplicative ones, with the multiplicative tensor distributing over the additive tensor.
